Sky Tomography for 3D Aerosol Distribution Recovery

### 2013-07-26 article.tex
Yoavs bookmark

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\mathbfcal{M}}
\newcommand{\Laplacian}{\mathbfcal{L}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ (units \si{\meter\squared}) for
interacting with the irradiance. The density of the particles is $n$
(units \si[sticky-per]{\per\cubic\metre}). Per unit volume, the {\em
  extinction coefficient} $\beta$ is
\begin{align}
  \beta= \sigma n \;.
  \label{eq:extinctc}
\end{align}
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential {\em optical
  depth}
\begin{align}
  d\tau= \beta dl=\sigma n dl \;.
  \label{eq:extinct}
\end{align}
The optical depth aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp(-\tau)
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
The angular distribution of scattering is determined by a {\em phase
  function} $P$. Part of the light scatters towards a camera's LOS, as
illustrated in \cref{fig:groundgrid}. The angle between the SR and LOS
is the scattering angle $\Phi^{\rm scatter}$. The phase function
$P(\Phi^{\rm scatter})$ is normalized: its integral over all solid
angles is unit. The {\em angular scattering coefficient}
$\tilde\alpha$ (units \si[sticky-per]{\per\meter\steradian}) is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

@@

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model:
\begin{align}
  P^{\rm air}\left[\mu(k)\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Consequently~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules can be modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4}
  \exp(-h/H^\mathrm{air}) %\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}

@@

We believe that high resolution atmospheric recovery can be achieved
by a set of ground-based wide-angle~\cite{Cossairt2011,
  Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
sky-cameras, looking upward, performing integral imaging of the sky.
Consider \cref{fig:groundgrid}.  Ground-based wide-angle sky-cameras
capture the sky lightfield from below. Per viewpoint, the view azimuth
and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bm{\Theta}}$.  A raw image is $i_{\bm
  c}({\bm{\Theta}})$: a camera's location ${\bm x}$ is fixed, while
any pixel in a frame represents an angle ${\bm{\Theta}}$.  The
measured radiance in all locations ${\bm x}$ and angles
${\bm{\Theta}}$ is the {\em lightfield} $I({\bm
  x},{\bm{\Theta}})$.This paper takes the first step, of formulating
this principle and demonstrating feasibility using realistic
simulations.  We simulate RT through the atmosphere using two
models. The first is based on Monte Carlo (MC) methods
(\cref{sec:monte-carlo-simul}) and models
Multiple-Scattering. Therefore it enables simulating realistic
scenarios.  The second model uses the Single-Scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than the MC model
but it enables stating an analytic solution to the RT in a closed
form. This closed form is beneficial to us as it enables us to invert
the model and thus recover the underlying atmosphere
(\cref{sec:inverse-problem}). To mimic realistic scenarios, we apply
the reconstruction algorithm on images simulated by the MC model.

@@

\section{Single-Scattering Model}
\label{sec:single-scatt-model}

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels).  A forward model takes as input the aerosol
distribution over the grid of voxels, and outputs images as if
captured at various viewpoints.  In a \emph{single-scattering} model,
any SR changes direction only once on the way to the camera. This
model is valid in atmospheres that are not very dense: inside fog and
clouds this model does not apply.  Under single-scattering
approximation, radiative transfer has three steps
(\cref{fig:groundgrid}):
\begin{inparaenum}[\hfill\bfseries a\upshape)]
\item \label{itm:first} Attenuation of a SR propagating from the top
  of the atmosphere (TOA) to voxel $k$.
\item \label{itm:second} Light scattering at voxel $k$, towards a
  camera.
\item \label{itm:third} Light attenuation on the LOS from voxel $k$ to
  the camera.
\end{inparaenum}
Steps \ref{itm:first} and \ref{itm:third} involve the optical depth
along the light path to and from voxel $k$, analyzed in
\cref{sec:optical-depth}.  Step \ref{itm:second} involves the
scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.

@@

Any voxel generally contains both air molecules and aerosols. Voxels
are indexed by $k$ or $q$. We assume that within any voxel, the
molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
corresponding to the value at each voxel center.

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$ (See
\cref{fig:groundgrid}). This SR intersects voxel $q$. The geometric
length of this intersection line segment is $l_{\rm SR}(q)$ which
depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.  We now define a
$N_{\rm voxels}\times N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun
    \rightarrow voxel}}$, whose element $(k,q)$ represents $l_{\rm
  SR}(q)$:
\begin{equation}
  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  \hspace{-0.05cm}
\end{equation}
Note that matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is
sparse.  Following \cref{eq:tau}, the optical depth between the TOA
and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation
\begin{equation}
  \vect{\tau}_{\rm SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}
  \label{eq:tau_matrix}
\end{equation}
Here $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack vector
representation of $\tau_{\rm SR}(k)$ and $\beta(q)$, respectively.

Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$ (see
\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
This LOS intersects voxel $q$. The geometric length of this
intersection line segment is $l_{\rm LOS_c}(q)$which depends on
$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
sparse matrix whose element $(k,q)$ is
\begin{equation}
  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      l_{{\rm LOS}_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}
The optical depth along a LOS to $k$ is
\begin{equation}
  \vect{\tau}_{{\rm LOS}_c} = \OpDistance^{\mathrm{voxel \rightarrow
      cam}} \vect{\beta}
  \label{eq:lLOSn}
\end{equation}
Here $\vect{\tau}_{\rm SR}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths of each voxel $k$ can
be joined to a single path from the TOA to camera $c$ giving
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:extinctc}, the total optical depths
corresponding to LOSs (of camera $c$) and SRs that cross all voxels
comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bm D}_c (\vect{\sigma} \odot {\bm n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product. This vector depends on the variables $\vect{\sigma}$ and
${\bm n}$, the aerosol extinction and density at each voxel
respectively.

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the
angular scattering coefficients across the domain are expressed in
vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,\quad
  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
    g}(\vect{\Phi}^{\rm scatter}_c)
  \label{eq:alpha_matrix}
\end{equation}
The vector ${\bm g}$ column-stacks the anisotropy parameter of the
phase function, in all voxels. We use this notation, to indicate a
parametric phase function as in \cref{eq:aerosol_scatter}.

@@

@@

In general terms, the variables are the set \mbox{$\left\{{\bm
      n},\left\{\vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm
        g}_{\lambda}\right\}_{\lambda}\right\}$} where $\lambda$
denotes the spectral (color) channel.  There are $N_{\rm spectral}$
spectral channels.  Thus, the number of unknown variables is in
principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm spectral})$}.

>>>>

%
% Some new commands I use in this text
%
\newcommand{\OpSphere}{\mathbfcal{S}}
\newcommand{\OpRot}{\mathbfcal{R}}
\newcommand{\OpDistance}{\mathbfcal{D}}
\newcommand{\OpCumsum}{\mathbfcal{C}}
\newcommand{\OpInt}{\mathbfcal{I}}
\newcommand{\OpCamera}{\mathbfcal{P}}
\newcommand{\Mask}{\bm{M}}
\newcommand{\OpDiag}[1]{\mathrm{diag}\left\{#1\right\}}
\newcommand{\Grad}[1]{\bm{\triangledown_{#1}}}
\newcommand{\argmin}{\mathrm{arg}\min}
\newcommand{\curly}[1]{\left\{#1\right\}}
\newcommand{\roundy}[1]{\left(#1\right)}
\newcommand{\recty}[1]{\left[#1\right]}
\newcommand{\PartDeriv}[2]{\frac{\partial{#1}}{\partial{#2}}}
\newcommand{\vect}[1]{\bm{#1}}
\newcommand{\mat}[1]{\bm{#1}}
\newcommand{\transpose}[1]{{#1}^\intercal}
\newcommand{\derivsym}[1]{\,d{#1}}
\newcommand{\yoavcomment}[1]{}
\renewcommand{\yoavcomment}[1]{#1} % Comment to remove images

@@

\noindent {\bf Extinction}: Sun rays (SR) irradiate a small volume
that includes particles of a certain type.  Each particle has an {\em
  extinction cross section} $\sigma$ for
interacting with the irradiance. The density of the particles is $n$. Per unit volume, the {\em extinction coefficient} is $\beta= \sigma n$.
The volume has infinitesimal length $dl$. Then, the relative portion
of extinct SR irradiance is the unitless differential optical
  depth, $d\tau= \beta dl=\sigma n dl$.
The {\em optical depth} aggregates in extended propagation:
\begin{align}
  \tau= \int d\tau=\int \beta dl=\int \sigma n dl \;.
  \label{eq:tau}
\end{align}
Through an attenuating volume, the {\em transmittance} exponentially
decays with the optical depth:
\begin{align}
  t=\exp(-\tau)
  \label{eq:beer-lambert}
\end{align}

\noindent {\bf Scattering}: Interaction of a single particle with the
irradiance is by absorption and scattering. The weight of scattering
(to all directions), relative to the total extinction is given by the
unitless {\em single scattering albedo} $\varpi$ of the particle. The
{\em scattering coefficient} $\alpha$ is
\begin{align}
  \alpha= \varpi\beta=\varpi \sigma n \;.
  \label{eq:alph}
\end{align}
The angular distribution of scattering is determined by a {\em phase
  function} $P$, which is normalized: its integral over all solid
angles is unit. Part of the light scatters towards a camera's LOS, as
illustrated in \cref{fig:groundgrid}. The angle between the SR and LOS
is the scattering angle $\Phi^{\rm scatter}$. The {\em angular scattering coefficient}
$\tilde\alpha$ is
\begin{align}
  \tilde\alpha(\Phi^{\rm scatter}) = \varpi\beta P(\Phi^{\rm scatter})
  = \varpi \sigma n P(\Phi^{\rm scatter}).
  \label{eq:alphabasic}
\end{align}

@@

\noindent {\bf Air molecules}: Scattering by air molecules follows the
{\em Rayleigh} model. The phase function is
\begin{align}
  P^{\rm air}\left[\mu\right] &\approx \sfrac{3}{16\pi}(1+\mu^2)
  \label{eq:rayleighP}
\end{align}
and the single scattering albedo is $\varpi^{\rm air}$=1. Air molecular density $n^{\rm air}$ falls
off approximately exponentially with altitude, with a
characteristic~\cite{Levi1980} falloff height $H^\mathrm{air}=8\
\si{\km}$. Thus~\cite{Levi1980}, the coefficients for
extinction and scattering by air molecules can be modeled by
\begin{align}
  \alpha^{\rm air}(h, \lambda)=\beta^{\rm air}(h, \lambda) \approxeq
  1.09 \times 10^{-3}\lambda^{-4}
  \exp(-h/H^\mathrm{air}) 
  \;,%\left[-\frac{h}{H^\mathrm{air}}\right].
  \label{eq:rayleighbeta}
\end{align}
where $\lambda$ is the wavelength, in microns.

@@

Consider a set of ground-based wide-angle cameras
 %~\cite{Cossairt2011, Peleg01omnistereo:panoramic, Koppal:2011:WMS:2191740.2192152}
looking upwards (\cref{fig:groundgrid}). The set performs {\em integral imaging}~\cite{integral} of the sky. Per viewpoint, the view azimuth and elevation angles (relative to the zenith and north) are
encapsulated in the vector ${\bm{\Theta}}$. Any camera $c$ is at a distinct fixed location ${\bm x}$, capturing raw image $i_c({\bm{\Theta}})$. This paper takes the first step, of formulating
a principle of recovering the 3D atmospheric aerosols distribution, using such data. To show feasibility, we perform radiative transfer using two different forward models, enabling cross-validation.
A forward model takes as input the 3D aerosol distribution, and outputs images as if
captured at various viewpoints. One model uses Monte Carlo (MC) methods (\cref{sec:monte-carlo-simul}): it is stochastic, slow but naturally expresses multiple-scattering. Hence, this approach simulates realistic
scenes of arbitrary complexity.  The second model uses the single-Scattering approximation
(\cref{sec:single-scatt-model}). It is less accurate than MC, but derives an analytic closed
form solution to the radiative transfer. This closed form enables simple inversion of 
the model, to estimate the underlying atmosphere (\cref{sec:inverse-problem}).

@@

\section{Single-Scattering Forward Model}
\label{sec:single-scatt-model}

The atmosphere is discretized into a grid of $N_{\rm voxels}$ volume
elements (voxels), indexed by $k$ or $q$. In a \emph{single-scattering} model,
any SR changes direction only once on the way to a camera. This
model is valid in atmospheres that are not very dense: inside fog and
clouds this model does not apply. In this model, radiative transfer has three steps
(\cref{fig:groundgrid}): ({\tt i}) Attenuation of a SR propagating from the top
  of the atmosphere (TOA) to voxel $k$. ~({\tt ii}) Light scattering at voxel $k$, towards a
  camera. ~({\tt iii}) Light attenuation on the LOS from voxel $k$ to
  the camera.~~
Steps~{\tt i},{\tt iii} involve the optical depth along the light path to and from voxel $k$, as analyzed in \cref{sec:optical-depth}.  Step~{\tt ii} involves the scattering coefficient at voxel $k$, described in
\cref{sec:scattering}.

@@

A voxel's vertical geometric thickness is $\Delta z$.  The Sun zenith
angle is $\Phi^{\rm SR}$. Denote a SR line segment between the TOA and
the center of voxel $k$ by $[{\rm SR},k]$ (See
\cref{fig:groundgrid}). This SR intersects voxel $q$. The intersection line segment has geometric
length $l_{\rm SR}(q)$, which depends on $\Delta z$, $\Phi^{\rm SR}$ and $q$.  Define a
$N_{\rm voxels}\times N_{\rm voxels}$ matrix $\OpDistance^{\mathrm{Sun
    \rightarrow voxel}}$, whose element $(k,q)$ represents $l_{\rm
  SR}(q)$:
\begin{equation}
  \OpDistance^{\mathrm{Sun \rightarrow voxel}}(k,q) =
  \left\{
    \begin{array}{ll}
      l_{\rm SR}(q) & \mbox{ if $q \in[{\rm SR},k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dsv}
    \end{array}
  \right.
  \hspace{-0.05cm}
\end{equation}
The matrix $\OpDistance^{\mathrm{Sun \rightarrow voxel}}$ is
sparse.  
Analogously, for camera $c$, denote by $[{\rm LOS}_c,k]$ a LOS bounded
between the camera and the center of voxel $k$ (see
\cref{fig:groundgrid}).  The LOS zenith angle is $\Phi^{\rm LOS}_c$.
Suppose this LOS intersects voxel $q$. The geometric length of this
intersection line segment is $l_{\rm LOS_c}(q)$ which depends on
$\Delta z$, $\Phi^{{\rm LOS}_c}$ and $q$.  Analogously to
\cref{eq:Dsv}, we define a $N_{\rm voxels}\times N_{\rm voxels}$
sparse matrix whose element $(k,q)$ is
\begin{equation}
  \OpDistance^{\mathrm{voxel \rightarrow cam}}_c(k,q) =
  \left\{
    \begin{array}{ll}
      l_{{\rm LOS}_c}(q) & \mbox{ if $q \in[{\rm LOS}_c,k]$} \\
      0  & \mbox{ otherwise}
      \label{eq:Dvc}
    \end{array}
  \right.
  .
  \hspace{-0.05cm}
\end{equation}

Any voxel generally contains both air molecules and aerosols.  We assume that within any voxel, the
molecular parameters $\{ \beta^{\rm air}(k),\alpha^{\rm air}(k)\}$ and
the aerosol parameters $\{ \sigma^{\rm aerosol}(k),\varpi^{\rm
  aerosol}(k), n^{\rm aerosol}(k),g(k)\}$ are constants, e.g.,
corresponding to the value at each voxel center.
Following \cref{eq:tau}, the optical depth between the TOA
and voxel $k$ is
\begin{equation}
  \tau_{\rm SR}(k)= \sum_{q \in[{\rm SR},k]} \beta(q) l_{\rm SR}(q) \;\;.
  \label{eq:lSRn}
\end{equation}
We can write \cref{eq:lSRn} using matrix notation,
  $\vect{\tau}_{\rm SR}=\OpDistance^{\mathrm{Sun \rightarrow voxel}} \vect{\beta}$,
where $\vect{\tau}_{\rm SR}$ and $\vect{\beta}$ are column stack vector
representations of $\tau_{\rm SR}(k)$ and $\beta(q)$, respectively. Similarly, 
the optical depth along a LOS to voxel $k$ is expressed by element $k$ of 
  $\vect{\tau}_{{\rm LOS}_c} = \OpDistance^{\mathrm{voxel \rightarrow
      cam}} \vect{\beta}$
Here $\vect{\tau}_{{\rm LOS}_c}$ is a column stack vector representation of
$\tau_{{\rm LOS}_c}(k)$.  The SR and LOS paths joining at each voxel can
form a single path from the TOA to camera $c$, yielding
\begin{equation}
  {\bm D}_c=
  {\bm D}^{\mathrm{Sun \rightarrow voxel}}+
  {\bm D}^{\mathrm{voxel \rightarrow cam}}_c
  \quad\text{ and }\quad
  \vect{\tau}_c=
  \vect{\tau}_{\rm SR}+
  \vect{\tau}_{{\rm LOS}_c}
  \;\;.
  \label{eq:D_tau_total}
\end{equation}

We discern between air molecules and other aerosols and therefore
write $ \vect{\tau}_c= \vect{\tau}_c^{\rm air} + \vect{\tau}_c^{\rm
  aerosol}$.  Using \cref{eq:rayleighbeta} for $\beta^{\rm air}$ in
all voxels, the vector $\vect{\tau}_c^{\rm air}$ is fixed. Thus
$\vect{\tau}_c^{\rm air}$ can be calculated once, per sun zenith
angle. Given \cref{eq:extinctc}, the total optical depths
corresponding to LOSs (of camera $c$) and SRs that cross all voxels
comprise the vector
\begin{equation}
  \vect{\tau}_c= \vect{\tau}_c^{\rm air}
  + {\bm D}_c (\vect{\sigma} \odot {\bm n})
  \;\;.
  \label{eq:tautotal}
\end{equation}
where the operator $\odot$ denotes the Hadamard (element-wise)
product. This vector depends on the variables $\vect{\sigma}$ and
${\bm n}$, the aerosol extinction and density at each voxel,
respectively.

@@

Per camera $c$ and voxel $k$, the lines $[{\rm SR},k]$ and $[{\rm
  LOS}_c,k]$ intersect at a fixed angle $\Phi^{\rm scatter}_c(k)$.
Column-stacking all voxels yields the vector representation of all
scattering angles in the domain, $\vect{\Phi}^{\rm scatter}_c$ per
camera $c$. Similarly, the single-scattering albdeos $\varpi^{\rm
  aerosol}$ in all voxels are stacked to vector $\vect{\varpi}$.
Using \cref{eq:alphabasic,eq:rayleighP}, the
angular scattering coefficients across the domain are expressed in
vector form by
\begin{equation}
  \tilde{\vect{\alpha}}^{\rm air}_c =
  \vect{\beta}^{\rm air} \odot P^{\rm air}(\vect{\Phi}^{\rm scatter}_c)\;,\quad
  \tilde{\vect{\alpha}}^{\rm aerosol}_c = \vect{\varpi}\odot
  \vect{\sigma} \odot {\bm n} \odot P^{\rm aerosol}_{\bm
    g}(\vect{\Phi}^{\rm scatter}_c) \;.
  \label{eq:alpha_matrix}
\end{equation}
The vector ${\bm g}$ column-stacks the aerosol anisotropy parameter of the
phase function, in all voxels. This notation indicates a
parametric phase function as in \cref{eq:aerosol_scatter}.

@@

\subsection{Unknowns and Prior Knowledge}
\label{sec:prior}

In general terms, the variables are the set
\begin{equation}
  {\cal V}\equiv
  \left\{
    {\bm n},
    \left\{
      \vect{\varpi}_{\lambda},\vect{\sigma}_{\lambda},{\bm g}_{\lambda}
    \right\}_{\lambda}
  \right\}
  \;\;,
  \label{eq:calV}
\end{equation}
where $\lambda$ denotes the spectral (color) channel.  There are
$N_{\rm spectral}$ spectral channels.  Thus, the number of unknown
variables is in principle \mbox{$|{\cal V}|=N_{\rm voxels}(1+3N_{\rm
    spectral})$}.

\subsection{Objective Function}
\label{sec:objective-function}

@@
